\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {R2 Telecomunications}{}
      {Systems Analyst - Intern}{Sep. 2017 - Dec. 2017}
      \resumeItemListStart
        \resumeItem{Spreadsheet Automation and BI Analysis}
          {Performed office tasks, provided support to new employees, created spreadsheets, and generated automated reports using VBA (MS Office). Analyzed data and conducted queries using Power Query and JavaScript (Google Drive).}
      \resumeItemListEnd

    \resumeSubheading
      {Quality Telecomunications}{}
      {Web Developer}{2018-2020}
      \resumeItemListStart
        \resumeItem{Java Web Development}
          {Developed web applications, websites, data analysis tools, and automated spreadsheets (macros using VBA for Office and javascript and typescript for Google Drive), among other IT-related tasks. Utilized JSF and JSP for Java web development and implemented unit tests with JUnit and Mockito to ensure code quality and functionality.}
      \resumeItemListEnd

    \resumeSubheading
      {Vasta Web}{}
      {Web Developer}{Jan. 2020 - Aug. 2020}
      \resumeItemListStart
        \resumeItem{E-commerce Development}
          {Developed and maintained e-commerce themes (Shopify) and built applications using Node.js (JavaScript and TypeScript).}
      \resumeItemListEnd

    \resumeSubheading
      {Neon Payments}{}
      {Mobile Developer - Android}{Sep. 2020 - Apr. 2024}
      \resumeItemListStart
        \resumeItem{Android Development}
          {Developed native Android applications using JavaRx, Gradle, Hilt, Jetpack, Coroutines, and other Android tools. Designed UI screens with XML and Jetpack Compose. Created and maintained an application with submodules, dependency injection, Firebase integration (remote config, events), and Mixpanel.}
        \resumeItem{Testing and Quality Assurance}
          {Conducted unit testing with JUnit, using Mockito and JaCoCo for mock and code coverage analysis. Automated testing processes within CI/CD pipelines to ensure application reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelancer}{}
      {Mobile Developer - Android}{Apr. 2024 - Today}
      \resumeItemListStart
        \resumeItem{Android Development}
          {Developed native Android applications using featured librarys such as Jetpack Compose and Flow. Implement services and broadcast using library as Exoplayer. Updates SDK versions setting permissions and fixing dependency errors. Refact legacy code (Java). Implement MVI Architecture. Create and maintaining unit test using JUnit, Mockito and automate with CI/CD pipelines (GitHub Actions).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
